%\documentclass{article}}
%
%\begin{document}
\documentclass[class=article, crop=false]{standalone}
\usepackage{00_Preamble/frr_preamble}
\usepackage{graphicx}
\usepackage[table,xcdraw]{xcolor}
\usepackage[normalem]{ulem}
\usepackage{longtable}
\usepackage{hyperref}
\usepackage{float}
\usepackage{graphics}
\usepackage{adjustbox}
\usepackage{placeins}

\begin{document}
	\subsection{Launch Field General Setup}
	\label{subsec:launch_field_general_setup}
	\subsubsection*{Necessary Hardware}
	\label{subsubsec:necessary_hardware}
	\begin{multicols}{2}
		\begin{todolist}
			\item Tent
			\item Tarps (2)
			\item Tables (2)
			\item Chairs (6)
			\item Garbage bags (2)
			\item X-frames (3)
			\item Robin's toolkit
			\item Electronics box
			\item Spare nuts and bolts and bolts bag
			\item Tape measure (2)
			\item Wire cutters
			\item Needle nose pliers
			\item Shears
			\item Zip Ties
			\item Metal file
			\item Box cutter
			\item Gorilla tape
			\item Sealant putty (blue) for sealing all holes between payload and electronics
			\item Epoxy kit (5-minute epoxy resin and hardener, mixing cups, popsicle sticks)
			\item Drill (with spare battery and bits)
			\item Sand paper
		\end{todolist}
	\end{multicols}
	
	\subsubsection*{Assembly Procedure}
	\textbf{Required Personnel:} Rocketry Mentor, Safety Officer (Robin, Taylor)
	\begin{todolist}		
		\item Unload equipment and materials from van. Bring to field setup location.
		\item Identify expected launch pad location, and begin field assembly at least 500 feet away.
		\item Set up tent and secure with stakes.
		\item Assemble portable tables. \textcolor{red}{\textbf{WARNING!} Ensure ground is level and clear from obstructions.}
		\item Set up bags for trash collection. \textcolor{red}{\textbf{WARNING!} Littering presents an environmental hazard.}
		\item Place X-frames for each section on tables.
		\item Place independent sections of rocket on X-frames (payload, avionics, tail).
		\item Place all electronics on their own table.
	\end{todolist}
	\bigbreak
	\bigbreak
	\textbf{Signatures:}
	\bigbreak
	Rocketry Mentor: \underline{\hspace{6cm}}
	\bigbreak
	\bigbreak
	Safety Officer: \underline{\hspace{6cm}}
	\end{document}